\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2014-10-08 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex

>>>>

\section{{\normalsize \label{sec:Using-SEP}}Using external SEP models.}

Stanford Exploration Project (SEP) models consists of two files per variables, one header file (\texttt{.H}) 
and one binary file (\texttt{.H$@$}). 
Among other information, the header file indicates, for each dimension, 
the offset (\texttt{o1}, \texttt{o2} and \texttt{o3} fields), 
the spatial step size (\texttt{d1}, \texttt{d2} and \texttt{d3} fields)
and the number of samples (\texttt{n1}, \texttt{n2} and \texttt{n3}) necessary to read
the linked binary file (\texttt{in} field).

SEP model reading occurs during database generation. It it the user responsibility
to ensure that proper interfaces between acoustic and elastic domains are set up
during the meshing phase. For more information, refer to 
section~\ref{cha:Running-the-Mesher-Meshfem3D}.

In \texttt{DATA/Par\_file}, \texttt{\textbf{MODEL}} should be set to \texttt{\textbf{sep}},
and \texttt{\textbf{SEP\_MODEL\_DIRECTORY}} should point to wherever your sep model files reside.

Note that in order not to overload the parameter file, SEP header files
should be named \texttt{vp.H}, \texttt{vs.H} and \texttt{rho.H}. The \texttt{in} field
in these binary files can be any path as long as it is relative to
the previously set \texttt{SEP\_MODEL\_DIRECTORY}.
We also assume that any dimensional value inside SEP header files is given in meters and
that binary files are single precision floating point numbers stored in little endian format.
There is currently only support for \texttt{vp}, \texttt{vs} and \texttt{rho} variables.

An example demonstrating the use SEP models is given in:
\texttt{EXAMPLES/meshfem3D\_examples/sep\_bathymetry}.
